Comparison of Catalogs

### 2024-07-17 compare/compare.qmd
Morph+Geom, Abs tabs

---
title: "Untitled"
format: html
bibliography: ../My_Library.bib
execute: 
  echo: true
  eval: true
---

@@

dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
dt.info()
```

```{python}
```

>>>>

---
title: "Comparison of Catalogs"
format: html
toc: true
toc-depth: 2
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: true
  eval: true
---

@@

dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
```

The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)`

## Comparable data

::: panel-tabset
## Coordinates

| LCV   | HECATE | Description     |
|-------|--------|-----------------|
| Ra_1  | RA_2   | Right Ascension |
| Dec_1 | DEC_2  | Declination     |
| Dis   | D      | Distance        |

## Velocities

| LCV               | HECATE                | Description                             |
|-------------------|--------------------|---------------------------------|
| W50 (with errors) |                       | H I line with at 50% level from maximum |
| RVel              | V (with errors)       | Heliocentric radial velocity            |
| Vm                |                       | Amplitude of rotational velocity        |
| VLG               | V/V_VIR (with errors) | Radial velocity                         |
| cz (with errors)  |                       | Heliocentric velocity                   |

## Morphology and Geometry

| LCV           | HECATE               | Description                                               |
|-----------------------|------------------------|-------------------------|
| TType         | T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |
| inc           | I                    | Inclination (deg)                                         |
| a26_1 (Major) | R1 (Semi-major axis) | angular diameter (arcmin)                                 |

## Luminosities

| LCV     | HECATE | Description |
|---------|--------|-------------|
| logKLum | logL_K |             |
|         |        |             |
|         |        |             |

## Magnitudes

| LCV                 | HECATE | Description |
|---------------------|--------|-------------|
| mag_B (with errors) |        |             |
| mag_FUV             |        |             |
|                     |        |             |

## Absorbsion

| LCV    | HECATE | Description                          |
|--------|--------|--------------------------------------|
| AB     |        | Galactic extinction in B band        |
| AB_int |        | Internal B band extinction           |
| AG     |        | Galactic absorption on B-band (mag)  |
| AI     |        | Intrinsic absorption on B-band (mag) |

## SFR

| LCV    | HECATE     | Description                                                      |
|--------------------|--------------------|--------------------------------|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
|        | logSFR_FIR | Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]   |
|        | logSFR_60u | Decimal logarithm of the 60um SFR estimate \[Msol/yr\]           |
|        | logSFR_12u | Decimal logarithm of the 12um SFR estimate \[Msol/yr\]           |
|        | logSFR_22u | Decimal logarithm of the 22um SFR estimate \[Msol/yr\]           |
|        | logSFR_HEC | Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]    |
|        | logSFR_GSW | Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]              |
| SFRFUV |            | FUV derived integral star formation rate                         |
| SFRHa  |            | H{alpha} derived integral star formation rate                    |

## Masses

| LCV            | HECATE   | Description                                               |
|--------------------|--------------------|--------------------------------|
| logM26         |          | Log mass within Holmberg radius                           |
| logMHI         |          | Log mass within Holmberg radius                           |
|                | logM_HEC | Decimal logarithm of the stellar mass \[Msol\]            |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
| logStellarMass |          | Stellar Mass from M\*/L=0.6                               |
:::
